{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}

### 2016-12-28 proposal/lipservice.tex
oh yeah, the most important part

{\bf Experimental goals.}
Having only one semester (ideally; or two, if my timeline ends up delayed) to test Landslide with Pintos students,
I'll not be able to assemble as comprehensive a dataset as I have with 15-410 at CMU.
This project will serve more as a proof-of-concept, demonstrating that model checking can realistically replace stress testing in operating systems courses worldwide.
Nevertheless, I intend also to analyze what little data I can gather, comparing the incidences and types of concurrency bugs found between Pebbles and Pintos populations.
This will perhaps shed light on the advantages and/or shortcomings of either project,
leading to recommendations for improving either project's educational value (independently of using MC).

>>>>

{\bf New emulation platform.}
Most importantly, I will need to free Landslide from its dependence on Simics, which requires paid licenses for use beyond CMU's walls.
Other candidate emulation (simulation or virtualization) platforms for Landslide include Bochs, QEMU, VMWare, and Xen.
I am presently studying which of these will most suit Landslide's needs,
but so far Bochs seems like the best bet, which happens to be the simulator used at Berkeley, Stanford, and U. of Chicago anyway.

{\bf Experimental goals.}
Having only one semester (ideally; or two, if my timeline ends up delayed) to test Landslide with Pintos students,
I'll be unable to gather as comprehensive a dataset as I have with 15-410 at CMU.
This will serve more as a proof-of-concept, demonstrating that MC can realistically replace stress testing in operating systems courses worldwide.
Nevertheless, I intend also to analyze what little data I can gather, comparing the incidences and types of bugs found between Pebbles and Pintos populations.
This will perhaps shed light on the advantages and/or shortcomings of either project,
leading to recommendations for improving either project's educational value (independently of using MC).
